### 2017-04-10 Manuscripts/cog-psych/cogpsych.tex
hotfix-- added domain param to conjugatejk13 model

@@

@@

\begin{figure}[p]
    \begin{center}
    \inputpgf{figs/}{range-diff-gradients.pgf}
    \caption{Behavioral and simulated relative range gradients. Each panel shows, for each stimulus, the dimensional orientation of the categories it was generated into: vertically aligned `columns' versus horizontally aligned `rows'.}
    \nbcnote{Need to run this on lando with many more samples}
    \label{fig:range-diff-gradients}
    \end{center}
\end{figure}

>>>>

A key distinction between PACKER and copy-and-tweak, as well as the the hierarchical sampling model, is that, of the three models, only PACKER is capable of making strong predictions about the location of new category members when the target class is entirely novel (i.e., no member of the category has been observed). Under these circumstances, there are no examples to copy, and thus the copy-and-tweak model predicts that items are generated at random. Likewise, with no observations on which to condition the mean of the category distribution, the hierarchical sampling model also picks an item at random. Thus, it is possible that the failure of these models is simply due to their inability to explain each participant's first trial (generating the first item in the `Beta' category). We conducted an identical set of simulations as above, excluding this trial

@@

\subsection{Category Location vs. Distributional Structure}

, in relation to what is already known. That is, when the target category is entirely novel (i.e., no member of the category has been observed), both copy-and-tweak and the hierarchical sampling model essentially generate items at random.

both the copy-and-tweak and hierarchical sampling models
The copy-and-tweak and hierarchical sampling models predictions about where new categories should be generated in relation to existing category members

\begin{figure}[p]
    \begin{center}
    \inputpgf{figs/}{range-diff-gradients.pgf}
    \caption{Behavioral and simulated relative range gradients. Each panel shows, for each stimulus, the dimensional orientation of the categories it was generated into: vertically aligned `columns' versus horizontally aligned `rows'.}
    \nbcnote{Need to run this on lando with many more samples. current = 30}
    \label{fig:range-diff-gradients}
    \end{center}
\end{figure}

@@

As noted in Experiments 1 and 2, we observed a great deal of individual differences in the types of categories generated. Within each condition, we observed tightly clustered and widely distributed categories, as well as row and column categories, and so forth. The simulations reported above serve to evaluate the models while considering the entire dataset, but a secondary goal of any formal account should be to provide some explanation of how different profiles of performance emerge. Many of the individual generation profiles we observed can be specifically targeted within the PACKER framework, simply by tuning the similarity trade-off parameter ($\gamma$) and the model's attention weights ($w$).

\nbcnote{manual description of how to get rows, columns, 4 corners, etc}

To systematically evaluate each model's ability to explain
